Modeling thermal dust emission with the {\it PLANCK} 2015 release maps

### 2015-06-22 ms.tex
added last couple of missing sentences to intro, still needs a lot of clean up

Even with the enhanced temperature resolution afforded by \PLANCK, 
systematic problems with both of these recent \PLANCK~based thermal dust 
emission models still remain. Further, no thermal dust emission model yet
exists based on the \PLANCK~2015 data release. Here we present an update
to the analysis of \cite{meisner15}, and create the first ever 100-3000 GHz
unpolarized thermal dust emission model based on the \PLANCK~2015 data release.
%But none of these are yet perfect. Mention CIBA and zodi as examples from
%Meisner + Finkbeiner. Also, no Planck 2015 release thermal dust model yet
%exists at all.

>>>>

Even with the enhanced temperature resolution afforded by \PLANCK, 
systematic problems with both of these recent \PLANCK~based thermal dust 
emission models still remain. Further, no thermal dust emission model yet
exists based on the \PLANCK~2015 data release. On large angular scales, 
imperfect zodical light corrections lead to the dominant systematic problem
in resulting \PLANCK~based reddening predictions \citep{meisner15}. The cosmic
infrared background anisotropies (CIBA) account for the majority of 
small-scale temperature and optical depth variation at high Galactic latitude.
Here we present an update to the analysis of \cite{meisner15}, and create the 
first ever 100-3000 GHz unpolarized thermal dust emission model based on the 
\PLANCK~2015 data release.
%But none of these are yet perfect. Mention CIBA and zodi as examples from
%Meisner + Finkbeiner. Also, no Planck 2015 release thermal dust model yet
%exists at all.
